Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

>>>>

Let us now focus on any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in  \J_k(R_1, ..., R_{k-2},$ $H, V)$. We classify the tuple into one of the two categories below:

\myitems{
    \item {{\bf Type 1:}} $h$ crosses all of $r_1, ..., r_{k-2}$, and $v$  crosses all of $r_1, ..., r_{k-2}$;

    \item {{\bf Type 2:}} $h$ or $v$ fails to cross some rectangle in $\set{r_1, r_2, ..., r_{k-2}}$. This means the existence of at least one rectangle $r_i$, for some $i \in [k-2]$, covers either an endpoint of $h$, or an endpoint of $v$, or both.
}
Figure~\ref{fig:hv:cats} illustrates a result tuple of each type, assuming $k = 4$.

\begin{figure} 
    \begin{tabular}{cc} 
        \includegraphics[height=27mm]{./artwork/cat1} & 
        \hspace{5mm} \includegraphics[height=27mm]{./artwork/cat2} \\
        (a) Cat.\ 1 result tuple & 
        (b) Cat.\ 2 result tuple
    \end{tabular}

    \figcapup 
    \caption{Two categories of H-V $k$-SJ result tuples ($k$ = 4)} 
    \label{fig:hv:types}
    \figcapdown
\end{figure}
